---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

**NOTE: This is work in progress.**

# gooddays

<!-- badges: start -->
<!-- badges: end -->



The goal of the package is to provide convenience functions for simple tasks that may be useful. 


## Installation

You can install the development version of gooddays from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mshmandal/gooddays")
```

## Usage

To split strings as vectors

```{r example_gd_split}
# load the package
library(gooddays)

# pass a string and split parameter based on which to split 
gd_split("ka,sui,moku",split=",")

# another example
gd_split("hello.world",split="\\.")
```

Convert a string to capitalize each word. Note this is just a wrapper for 'tools::toTitleCase()'. The goal here is to gather and write such common convenience functions for repeated use.

```{r example_gd_title}
library(gooddays)
gd_title("hello world")

# which can be done by tools::toTitleCase() function
tools::toTitleCase("hello world")

# trivial example
data(cars)

plot(
  cars,
  xlab=gd_title(names(cars)[1]),
  ylab=gd_title(names(cars)[2])
  )
```


